### 2021-06-18 paper/appendix_results.tex
Add rapid test statistics with new layout.

\subsection{Rapid Tests \comment[id=K]{The figures will likely change layout later}}
\label{subsec:appendix_rapid_tests}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/demand_shares}
  \caption{Share of the Population Demanding a Rapid Test for a Particular Reason}
  \label{fig:rapid_tests_by_reason}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without
  PCR demand and other contact demand together form the private demand category. Also
  note that these do not add up to the total share of demanded rapid tests as individuals
  may have more than one reason to demand a rapid test on any given day. }
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_demand}
  \caption{Share of individuals who Demand a Rapid Test for a Particular Reason that are Actually Infected}
  \label{fig:share_of_rapid_tests_by_reason_by_infected}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without
  PCR demand and other contact demand together form the private demand category. Also
  note that this is not the same as individuals getting a positive rapid test. The
  sensitivity is quite low before individuals become infectious. Therefore, if
  individuals are still in the latent period of their infection they are likely to get a
  false positive rapid test.}
\end{figure}

>>>>

\subsection{Rapid Tests}
\label{subsec:appendix_rapid_tests}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/educ_demand_share}
    \caption{Share of the Population Demanding a Rapid Test in an Education Setting}
    \label{fig:educ_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/work_demand_share}
    \caption{Share of the Population Demanding a Rapid Test due to Work}
    \label{fig:work_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/private_demand_share}
    \caption{Share of the Population Demanding a Rapid Test for Private Reasons}
  \label{fig:private_rapid_test_demand}
  \end{subfigure}
  \caption{Rapid Test Demand by Reason}
  \label{fig:rapid_test_demand_by_reason}
  \floatfoot{\noindent \textit{Note:}
    Rapid tests in the education setting are demanded by teachers (nursery, preschool and
    school) as well as school pupils. After Easter the required frequency of tests is
    increased from once per week to twice per week. Work rapid tests are demanded by
    individuals that still have work contacts, i.e. do not work from home. The share of
    employers offering rapid tests increases over the time frame and the frequency of
    testing is also increased. Tests are demanded by individuals for one of three private
    reasons: having developed symptoms without access to a PCR test, having a household
    member that has tested positive or developed symptoms or having planned weekly
    meeting with friends.
  }
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_educ_demand}
    \caption{Share of Rapid Tests in the Educational Setting Demanded by Infected
    Individuals}
    \label{fig:share_infected_among_educ_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_work_demand}
    \caption{Share of Work Rapid Tests Demanded by Infected Individuals}
    \label{fig:share_infected_among_work_rapid_test_demand}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_private_demand}
    \caption{Share of Private Rapid Tests Demanded by Infected Individuals}
  \label{fig:share_infected_among_private_rapid_test_demand}
  \end{subfigure}
  \caption{Share of Rapid Tests Demanded by Infected Individuals by Reason}
  \label{fig:share_infected_among_rapid_test_demand_by_reason}
  \floatfoot{\noindent \textit{Note:}
    Rapid tests in the education setting are demanded by teachers (nursery, preschool and
    school) as well as school pupils. After Easter the required frequency of tests is
    increased from once per week to twice per week. Work rapid tests are demanded by
    individuals that still have work contacts, i.e. do not work from home. The share of
    employers offering rapid tests increases over the time frame and the frequency of
    testing is also increased. Tests are demanded by individuals for one of three private
    reasons: having developed symptoms without access to a PCR test, having a household
    member that has tested positive or developed symptoms or having planned weekly
    meeting with friends. Private rapid tests have a very high share of infected
    individuals because they are mostly triggered by events that make infection likely.
    Remember however, that one reason is that a household member has a positive rapid
    test. This means that work and education rapid tests which have a low rate of
    infected individuals trigger more targeted rapid tests. They also have a much higher
    volume of tests. As can be seen in the decomposition (see
    Figure~\ref{fig:2021_scenarios_decomposition_tests} every category of tests is
    important for the overall effect.}
\end{figure}
